\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Mike Hoyt}}\\
	Milwaukee, WI $\cdot$ hoyt.mich@gmail.com $\cdot$ (608)449-8644\\
\end{center}


%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Thomson Reuters} \hfill Brookfield, WI\\
\textit{Technical Lead} \hfill April 2017 | June 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Led a team of 3 responsible for architecting and implementing the shared libraries and general design of the company\textquotesingle{}s next generation RESTful microservices in .NET Core.
	\item Reduced the time and experience necessary to develop new microservices by creating a generator to set up user authentication/authorization, structured logging, metrics and internal API connections.
	\item Oversaw development of all microservices, ensuring proper REST standards and above 90\% code coverage.
	\item Gave a training presentation to 20 developers on developing RESTful APIs with .NET Core.
\end{itemize}
\vspace{-1mm}
\textit{Software Engineer} \hfill June 2015 | April 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Collaborated with developers across 2 teams and 12 Silverlight web applications to develop new front-end and back-end features for trading/managing equities, mutual funds and options. The applications are part of Thomson One BETA Systems, a platform responsible for roughly 1/3 of the trades through the NYSE.
	\item Created reusable and dynamic performance, load and integration test scripts in JMeter to ensure reliable deployments of our REST and SOAP APIs.
	\item Implemented unit-test frameworks on all untested C\# applications. Gave training to other developers on how to safely make changes to applications by refactoring legacy code   for testability.
	\item Redesigned the order entry portion of Thomson One Anywhere, the organization's flagship mobile trading solution, to conform to platform-wide whitelabeling standards, while making it responsive across all screen sizes.
	\item Transformed how internship interviews are conducted by applying coding tests. Co-mentored 2 software engineering interns, teaching SDLC best practices.
\end{itemize}
\vspace{-1mm}
\textit{Software Engineer Intern} \hfill June 2014 | August 2014\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Developed front-end freatures for a Silverlight stock trading application used by 60,000 financial advisors.
\end{itemize}

%==== International Experience ====%
\header{Other Experience}
\vspace{1mm}

\textbf{International Travel} \hfill June 2017 | June 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Independently traveled through 31 countries in Europe, Asia and Oceania.
	\item Gained self-confidence and a strong appreciation for diversity.
\end{itemize}

%==== Education ====%
\header{Education}
\textbf{University of Wisconsin - La Crosse}\hfill La Crosse, WI\\
BS Computer Science | Minor in Mathematics \textit{GPA: 3.6} \hfill September 2011 | June 2015\\
\vspace{2mm}
\textbf{Anglo American University}\hfill Prague, Czech Republic\\
BS Computer Science \textit{GPA: 4.0} \hfill February 2014 | June 2014\\
\vspace{2mm}

\header{Skills}
\begin{tabular}{ l l }
	Programming Languages: & C\#, Java, Python, HTML, CSS, JavaScript (familiar), SQL (familiar)               \\
	Frameworks/Technologies:            & .NET Core, .NET WebAPI, Silverlight, JMeter, Git, SVN, Jenkins, \\
	& Windows, Linux, AngularJS (familiar) \\ 
\end{tabular}
\vspace{2mm}







\ 
\end{document}